### 2019-11-20 Manuscript/Manuscript.tex
Updates from Overleaf

\noindent
% MAXIMUM 125 CHARACTERS 
\textbf{One Sentence Summary:} Arc-continent collision in the Southeast Asian islands increased global weatherability enough to drive Neogene cooling.

@@

The Southeast Asian islands (SEAI) have an out-sized contribution to modern chemical weathering fluxes. The confluence of steep topography, a warm and wet tropical climate, and the presence of mafic lithologies results in high fluxes of Ca and Mg cations and associated \COtwo consumption \cite{Gaillardet1999a}. There has been a significant increase of subaerially-exposed land area within the region since the Miocene associated with ongoing arc-continent collision between Australia and the Sunda-Banda arc system \cite{Molnar2015a, Macdonald2019a}. Concurrently, after the Miocene Climatic Optimum, a cooling trend began ca. 15~Ma and accelerated over the past 4 million years (m.y.) culminating with the onset of Northern Hemisphere glaciation \cite{Zachos2001a}. Many hypotheses have been proposed to explain this cooling trend including changes in ocean/atmosphere circulation \cite{Haug1998a, Shevenell2004a, Molnar2015a}, a decrease in volcanic outgassing \cite{Berner1983a}, or uplift in the Himalaya \cite{Raymo1992a}. Here we instead propose that SEAI emergence was itself sufficient to explain long-term climatic cooling over the Neogene.

@@

>>>>

\noindent
% MAXIMUM 125 CHARACTERS 
\textbf{One Sentence Summary:} The growth of tropical maritime islands led to efficient carbon consumption and drove cooling over the past 15 million years.

@@

The Southeast Asian islands (SEAI) have an out-sized contribution to modern chemical weathering fluxes. The confluence of steep topography, a warm and wet tropical climate, and the presence of mafic lithologies results in high fluxes of Ca and Mg cations and associated \COtwo consumption \cite{Gaillardet1999a}. There has been a significant increase of subaerially-exposed land area within the region since the Miocene associated with ongoing arc-continent collision between Australia and the Sunda-Banda arc system \cite{Molnar2015a, Macdonald2019a}. Concurrently, after the Miocene Climatic Optimum, a cooling trend began ca. 15~Ma and accelerated over the past 4 million years (m.y.) culminating with the onset of Northern Hemisphere glaciation \cite{Zachos2008a}. Many hypotheses have been proposed to explain this cooling trend including changes in ocean/atmosphere circulation \cite{Haug1998a, Shevenell2004a, Molnar2015a}, a decrease in volcanic outgassing \cite{Berner1983a}, or uplift in the Himalaya \cite{Raymo1992a}. Here we instead propose that SEAI emergence was itself sufficient to explain long-term climatic cooling over the Neogene.

@@

It continues to be argued that hypotheses that invoke enhanced weathering in regions of active uplift predict an increase in global alkalinity fluxes \cite{Si2019a}. However, total alkalinity delivery through silicate weathering needs to be nearly constant when considering the requirement of steady-state for the long-term carbon cycle. Rather, when weathering is enhanced in a region such as the emerging SEAI, the decrease in \pCOtwo results in a decrease in chemical weathering in other regions where there has not been tectonically-forced change. The same alkalinity delivery occurs more efficiently and thereby at lower \pCOtwo. Given that the weathering of carbonate is disconnected from long-term carbon-cycle mass balance, alkalinity delivery through carbonate weathering could change in an evolving climate and be observable in proxy records \cite{Si2019a}.
